\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2013-11-03 doc/paper.tex
added more to introduction.

%macros
\newcommand{\sarah}{SARAH\xspace}
\newcommand{\fs}{FlexibleSUSY\xspace}

\newcommand{\code}[1]{\lstinline|#1|}  % inline source code
\newcommand{\textoverline}[1]{$\overline{\mbox{#1}}$}
\newcommand{\DRbar}{\textoverline{DR}}  % inline source code

@@

@@

\section{Stucture of the spectrum generator}
\subsection{boundary conditions}
Different types, how we match to low energy data.  reference EWSB or merge that section here.
\subsection{RGEs}
\subsection{tree level spectrum}
\subsection{Electroweak symmetry breaking}
\subsection{pole masses}
\subsection{two scale fixed point iteration}
\subsection{Lattice method}
If ready.
\subsection{multiple effective models at different scales}
\section{Implementing new models}
\section{Adapting the code at the C++ level}
\appendix
\section{Examples}
\section{Tests}

@@

>>>>

%macros
\newcommand{\sarah}{SARAH\xspace}
\newcommand{\fs}{FlexibleSUSY\xspace}
\newcommand{\ESSM}{E$_6$SSM\xspace}
\newcommand{\code}[1]{\lstinline|#1|}  % inline source code
\newcommand{\textoverline}[1]{$\overline{\mbox{#1}}$}
\newcommand{\DRbar}{\textoverline{DR}}  % inline source code

@@

\subsection{The Program}
\fs is a MATHEMATICA package designed to create a fast and easily
adaptable spectrum generator in C++ for any SUSY model and some
non-supersymmetric models {\color{red} can we?}.  \fs makes use of the
existing \sarah package to obtain one-loop self energies, one-loop
tadpoles corrections and two-loop renormalisation group
equations(RGEs) in any model.  \fs then converts these algerbraic
expressions from \sarah into C++ code using the C++11 standard. \fs
uses some parts of SOFTSUSY\cite{Allanach:2001kg}, the very fast Eigen
library \cite{eigen}, as well as the gnu scientific library and the
boost library to create numerical routines which then use these
routines to solve the RGEs and EWSB conditions which will be used in
the spectrum generator. The main solver routine of \fs then calls
these routines to find simultaneous solutions for the EWSB, low energy
data, and other, user supplied, boundary conditions (e.g. the usual
mSUGRA universality conditions) and calculates the mass spectrum.

 The modular structure of the generated code allows for any individual
 components to be replaced with an alternative if available.  Indeed
 \fs has been intentionally designed to grow as alternative solvers
 and calculators are added and a subsequent release with an
 alternative lattice solver is already planned.{\color{red} Or Indeed
   flexible SUSY is distributed with two diffrent main solvers, the
   two-scale solver based omn the approach of \cite{} and designed for
   speed and the a lattice solver designed to solve tricky cases where
   the fixed point iteration of the two-scale approach fails to
   converge.}

@@

\section{Stucture of the spectrum generator}
\subsection{boundary conditions}
Different types, how we match to low energy data.  reference EWSB or merge that section here.
\subsection{RGEs}
\subsection{tree level spectrum}
\subsection{Electroweak symmetry breaking}
\subsection{pole masses}
\subsection{two scale fixed point iteration}
\subsection{Lattice method}
If ready.
\subsection{multiple effective models at different scales}
\section{Implementing new models}
\section{Adapting the code at the C++ level}
\appendix
\section{Examples}
\subsection{NMSSM}
Detailed steps to create NMSSM model file.
\subsection{\ESSM}
Detailed steps to create \ESSM model file.

\section{Tests}

@@

\bibitem{eigen}
Eigen library, version 3.1 \url{http://eigen.tuxfamily.org}
